R Notebook

### 2017-11-02 doc/RMD/wmn-differentiation.Rmd
add DA screeplot to show absolutely nothing

```{r dapc, fig.width = 5, fig.height = 4.5}
setPop(bebug) <- ~Host
bebug_dapc <- dapc(bebug, n.pca = 20, n.da = 2)
scatter(bebug_dapc, #clabel = 0,
        legend = TRUE,
        scree.pca = TRUE, 
        scree.da = FALSE,
        col = viridis::plasma(3, end = 0.85),
        bg.inset = "grey90",
        bg = "grey90")

>>>>

```{r dapc, fig.width = 5, fig.height = 4.5}
setPop(bebug) <- ~Host
bebug_dapc <- dapc(bebug, n.pca = 20, n.da = 2)
scatter(bebug_dapc, #clabel = 0,
        legend = TRUE,
        scree.pca = TRUE, 
        scree.da = TRUE,
        col = viridis::plasma(3, end = 0.85),
        bg.inset = "grey90",
        bg = "grey90")
